On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-09-06 Manuscript/manuscript.tex
Updated the inclusion of 2023 data explanation

There are two types of data that are explored throughout this paper: data from
1999-2023 for every world championship, and data from athletes who competed in
the 2022 World Championships and another competition (either 2019 World 
Championships, 2023 World Championships or a 2022 national competition typically
held within three months of the 2022 World Championships). 
%\eds{is this true? are you still using the 2019 world championships data for the
%rank-based analyses, or only the national competitions?}
%\of{Yes the ranked based comparison has 2 subsections: 2022 national vs 2022
%international and 2019 international vs 2022 international.  Should I instead say
%that there are three types of data across 2 sections or something like that?}
%\eds{I think this is fine here, but it is not at all clear that there are two
%subsections in the rank-based results for 2022 national vs 2022
%international and 2019 international vs 2022 international.}
%\of{Currently under the Methods/Results section I have GLMM and rank based comparison
%do you think I need subsections under rank based comparison, or is that too much
%compartmentalization?  Or should I instead say there are 3 types of data that are
%used in two different methods, or something like that?} \eds{I prefer
%subsections within rank-based comparison.}
The first data set is used for the GLMM analysis described in 
Section~\ref{sec:glmm}, while the second collection of data is used for the 
rank-based comparisons described in Section~\ref{sec:rank}.  This paper was
started before the 2023 World Championships, but as that data has become
available recently, we are pleased to include it in our analysis.

>>>>

There are two types of data that are explored throughout this paper: data from
1999-2023 for every world championship, and data from athletes who competed in
the 2022 World Championships and another competition (either 2019 World 
Championships, 2023 World Championships or a 2022 national competition typically
held within three months of the 2022 World Championships). 
%\eds{is this true? are you still using the 2019 world championships data for the
%rank-based analyses, or only the national competitions?}
%\of{Yes the ranked based comparison has 2 subsections: 2022 national vs 2022
%international and 2019 international vs 2022 international.  Should I instead say
%that there are three types of data across 2 sections or something like that?}
%\eds{I think this is fine here, but it is not at all clear that there are two
%subsections in the rank-based results for 2022 national vs 2022
%international and 2019 international vs 2022 international.}
%\of{Currently under the Methods/Results section I have GLMM and rank based comparison
%do you think I need subsections under rank based comparison, or is that too much
%compartmentalization?  Or should I instead say there are 3 types of data that are
%used in two different methods, or something like that?} \eds{I prefer
%subsections within rank-based comparison.}
The first data set is used for the GLMM analysis described in 
Section~\ref{sec:glmm}, while the second collection of data is used for the 
rank-based comparisons described in Section~\ref{sec:rank}.  This paper was
started shortly after the 2022 World Championships, but as the 2023 data has 
become available recently, we are pleased to include it in our analysis, and it
did not significantly change our results.
